---
title: "SII"
author: "Christopher W Bishop"
date: "10/25/2015"
output: html_document
---

```{r}
library(readxl)
library(dplyr)
library(ggplot2)
library(GGally)

data = read_excel('For SPSS2.xlsx')

# Add site information and clean data a bit
data =
  data %>%
  filter(!is.na(subject_id)) %>% # remove what look to be bogus entries
  filter(subject_id>1010) %>%
  mutate(site=ifelse(subject_id>=1999, 'UofI', 'UW'))

# Impute missing values
#   A bit quick-and-dirty, but a decent starting place.
#   Fills in missing values with the site-specific mean.
data = 
  data %>% 
  group_by(site) %>%
  mutate_each(funs(ifelse(is.na(.), mean(., na.rm=TRUE), .)))

# Need SII values.
data = data %>% filter(!is.na(AverageSII) & !is.na(BestSII))

```

```{r, fig.cap='SII vs. APHAB'}
# Start with pairwise plots
ggpairs(data %>% select(BestSII, AverageSII, contains('aphab')), color='site')
```

This is a bit overwhelming to look at, but some decent takeaways.

- APHAB categories are generally correlated with each other. So dimensionality reduction likely necessary (e.g., PCA via SVD)
- There are a number of outliers we'll need to deal with.
    - Seem to be more outliers at UofI than UW.
    - May need to transform data
- Sites are *generally* comparable.

```{r, fig.cap='SII vs. SADL'}
ggpairs(data %>% select(BestSII, AverageSII, contains('sadl')), color='site')
```

- sadl_nf may be correlated with best 
- Several f the sadl metrics are correlated (so redundant information captured in each).

```{r, fig.cap='SII vs. DOSO'}
ggpairs(data %>% select(BestSII, AverageSII, contains('doso')), color='site')
```

- Again, there are outliers we'll need to deal with, particularly at UofI
    - See dosoa_us. What to do with those massive outliers?
- Again, subscores are correlated. This will be a pain to work through.

```{r, fig.cap='SII vs. Aided HHIE'}
ggpairs(data %>% select(BestSII, AverageSII, contains('HHIE')), color='site')
```

```{r, fig.cap='SII vs. IOIHA'}
ggpairs(data %>% select(BestSII, AverageSII, contains('ioiha')), color='site')
```

- Eek, outliers galore!